Towards a Machine Learning approach for Aggregate Computing

### 2021-07-16 paper-2021-woa-ac-ml.tex
minors
minors on section outline

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  Cyber-Physical System \sep
  Aggregate Computing \sep
  Deep Learning \sep
  Reinforcement Learning \sep
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
\todo[inline, color=red]{max pages : 16}
\section{Introduction}
Aggregate Computing~\cite{DBLP:journals/computer/BealPV15}
\todo[inline]{walkthrogh Cyber Physical Systems, why they are hard}
\todo[inline]{Brief description of declarative approach, pros and cons}
\todo[inline]{Brief description of machine learning approach (MARL and GNN for communication), pros and cons}
\todo[inline]{Declare our direction: Combination to declarative and automatic approach}
\todo[inline]{Outline}

\section{Background and Related Work}
\todo[inline]{walkthrogh traditional engineering way to design CPS}
\todo[inline]{walkthrogh Aggregate Computing}
\todo[inline]{walkthrogh Machine learning approach applied in MARL}
\todo[inline]{current limitation (application specific, not large scala, centralised in some cases,..)}
\todo[inline]{novel work on GNN -- agent learn to communicate -- node size indipendent~\cite{DBLP:conf/corl/TolstayaGPP0R19}}

@@

\section{Toward a Neural Network Model}
\todo[inline]{declare inspiration of GNN} %%ideally, we should use either reinforcement and supervised learning
\todo[inline]{show the structure: state network, neighbour network, output network}
\todo[inline]{possible limitations: non stabilisation and asynchrnous evaluation}
\todo[inline]{learning algorithm: how to apply backprop here (similar to truncated backpropagation, currently does not work)}

\section{Evaluation} %% optional section
\todo[inline]{define experiment setup}
\todo[inline]{verify if the system perform as traditional method}

>>>>

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  Collective-Adaptive System \sep
  Aggregate Computing \sep
  Deep Learning \sep
  Reinforcement Learning \sep
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
\todo[inline, color=red]{max pages : 16}
\section{Introduction}
Aggregate Computing~\cite{DBLP:journals/computer/BealPV15}
\todo[inline]{walkthrogh Cyber Physical Systems, why they are hard}
\todo[inline]{Brief description of declarative approaches, pros and cons}
\todo[inline]{Brief description of machine learning approaches (MARL and GNN for communication), pros and cons}
\todo[inline]{Declare our direction: Combination to declarative and automatic approach}
\todo[inline]{Outline}

\section{Background and Related Work}
\todo[inline]{walkthrogh traditional engineering way to design CPS}
\todo[inline]{walkthrogh Aggregate Computing}
\todo[inline]{walkthrogh Machine learning approach applied in MARL}
\todo[inline]{current limitation (application specific, not large scale, centralised in some cases,..)}
\todo[inline]{novel work on GNN -- agent learn to communicate -- node size indipendent~\cite{DBLP:conf/corl/TolstayaGPP0R19}}

@@

\section{Towards Machine Learning approaches}
\todo[inline]{declare inspiration of GNN} %%ideally, we should use either reinforcement and supervised learning
\todo[inline]{show the structure: state network, neighbour network, output network}
\todo[inline]{possible limitations: non stabilisation and asynchrnous evaluation}
\todo[inline]{learning algorithm: how to apply backprop here (similar to truncated backpropagation, currently does not work)}
\todo[inline]{when makes sense to apply RL? (goal-oriented application?)}
\section{Evaluation} %% optional section
\todo[inline]{define experiment setup}
\todo[inline]{verify if the system perform as traditional method}
